### 2014-05-02 Article.tex
Article Abstract+Intro+Conjecture

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.0in]{geometry}
\usepackage[british]{babel}
\usepackage{indentfirst}
\usepackage{array,booktabs,longtable}
\usepackage{multirow}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{amsmath}

@@

@@

In a second step, we show how we proved this conjecture for $n$ from 1 to 6, and how we demonstrated that the number of comparisons is an upper bound of the optimal number of boxes 
for $n$ from 7 to 13 by optimizing the checking algorithm and by constructing a precise configuration.

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.0in]{geometry}
\usepackage[british]{babel}
\usepackage{indentfirst}
\usepackage{array,booktabs,longtable}
\usepackage{multirow}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{url}

@@

\newtheorem*{Conj*}{Conjecture}

@@

In a second step, we show how we proved this conjecture for $n$ from 2 to 6, and how we demonstrated that the number of comparisons is an upper bound of the optimal number of boxes 
for $n$ from 7 to 13 by optimizing the checking algorithm and by constructing a precise configuration.

@@

% Part 0. Introduction
% Part 1. Conjecture
% Part 2. Optimisation
% Part 3. Pistes de recherche

\section{Our conjecture}

To understand the problem, we first tried manually to get $opt_n$ for very small values of $n$.\\
For $n=2$, the answer is quite simple~: One box is enough and necessary to swap the two wires.\\
For $n=3$, two boxes aren't enough. Using a permutation, we can consider that the first box swap the wires 1 and 2, and that the second box swap the wires 2 and 3.
Then the permutation $(1,3)$ can't be generated with this configuration. Hence, we have $opt_3=3$.

For greater values of $n$, we implemented a naive and brutal algorithm that for $k$ given, creates all the possible configurations of $k$ boxes, 
and checks if one of these configurations is valid. We first try it with $opt_{n-1}+1$. Then,  we increment $k$ and try again until we get a valid configuration.
With this algorithm, we easily get $opt_n$.\\
However, this only works for small values of $n$. For $n$ greater than 6, we lack memory and time to achieve the computation.

Using this algorithm, we got the following results~:

\begin{tabular}{|c|c|}
\hline
Number of wires $n$ & $opt_n$ \\
\hline
2 & 1 \\
3 & 3 \\
4 & 5 \\
5 & 8 \\
6 & 11 \\
\hline
\end{tabular}\\

According to the fact that this sequence is exactly the beginning of the sequence A001855 of the Encyclopedia of Integer Sequences\footnote{The On-Line Encyclopedia of Integer Sequences, Sorting numbers: maximal number of comparisons for sorting n elements by binary insertion, \url{http://oeis.org/A001855}}, 
corresponding to the maximal number of comparisons for sorting $n$ elements by binary insertion, we guessed that these sequences were equal.

\Large
\begin{Conj*}
$opt_n$ is equal to the maximal number of comparisons for sorting $n$ elements by binary insertion.
\end{Conj*}
\normalsize

In order to prove this conjecture for greater values, we tried to optimize our checking algorithm. That will be described in the next part.

\section{Hypothesis box system}

\subsection{The basis set}

\subsection{Truncation}

\subsection{Testing the box system}

\subsection{Useless box elimination}
